### 2018-11-06 pilot_manuscript.Rmd
little more - hoping to start valence section in the morning

This issue is compounded by the fact the Moral Foundations Questionnaire and its subscales assume endorsement lies on a continuum.

>>>>

This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum. One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@GILLIGAN1991]. The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6. While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation. When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@GILLIGAN1991]. This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.
